---
title: "Promotion"
author: "CoreyJackson"
date: "11/24/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(Rmisc)
library(psych)
library(plyr)
library(dplyr)
library(magrittr)
library(ggthemes)
library(scales)

classifications_promotion <- read.csv("~/Dropbox/INSPIRE/Data/Promotion Analysis/classifications_promotion.csv")

```

## Promotion Analysis for Gravity Spy Users

Data taken from October 12 2016 - November 1 2016

```{r setup2, include=FALSE}
classifications_promotion$SubmitLevel[classifications_promotion$workflow == "1610"] <- "Neutron Star Mountain (NSM)"
classifications_promotion$SubmitLevel[classifications_promotion$workflow == "1934"] <- "Galactic Supernova (GS)"
classifications_promotion$SubmitLevel[classifications_promotion$workflow == "1935"] <- "Neutron Star Merger (NSM2)"
classifications_promotion$SubmitLevel[classifications_promotion$workflow == "2360"] <- "Black Hole Merger (BHM)"
classifications_promotion$SubmitLevel[classifications_promotion$workflow == "2117"] <- "Universe Cosmic Background (UCB)"

```

Summary statistics for users. 

1610: Neutron Star Mountain  
1934: Galactic Supernova  
1935: Neutron Star Merger  
2360: Black Hole Merger  
2117: Universe Cosmic Background  

```{r pressure, echo=FALSE}

classifications_promotion$UserLevel <- factor(classifications_promotion$UserLevel, levels= c("Neutron Star Mountain","Galactic Supernova","Neutron Star Merger","Black Hole Merger","Universe Cosmic Background"))
  
promotions_stats <- ddply(classifications_promotion, c("UserLevel"),summarise,
	Users = length(unique(login)),
	NSM = sum(SubmitLevel=="Neutron Star Mountain (NSM)"),
	GS = sum(SubmitLevel=="Galactic Supernova (GS)"),
	NSM2 = sum(SubmitLevel=="Neutron Star Merger (NSM2)"),
	BHM = sum(SubmitLevel=="Black Hole Merger (BHM)"),
	UCB = sum(SubmitLevel=="Universe Cosmic Background (UCB)"))

promotions_stats2 <- ddply(classifications_promotion, c("UserLevel"),summarise,
	Users = length(unique(login)),
	Class_Mean = mean(Classifications),
	Class_Med = median(Classifications),
	Sess_Mean = mean(Session),
	Sess_Med = median(Session)
	)

promotions_stats3 <- ddply(classifications_promotion, c("login","UserLevel"),summarise,
	Level_Classifications = length(login),
	Min_Classification = min(Classifications),
	Max_Classification = max(Classifications),
	Session_Achieved = min(Session),
	Max_Session = max(Session),
	NSM = sum(SubmitLevel=="Neutron Star Mountain (NSM)"),
	GS = sum(SubmitLevel=="Galactic Supernova (GS)"),
	NSM2 = sum(SubmitLevel=="Neutron Star Merger (NSM2)"),
	BHM = sum(SubmitLevel=="Black Hole Merger (BHM)"),
	UCB = sum(SubmitLevel=="Universe Cosmic Background (UCB)")
	)

df.summary = classifications_promotion %>% group_by(SubmitLevel, UserLevel) %>% 
  summarise(Classifications = length(Classifications)) %>%   # Within each Brand, sum all values in each Category
  mutate( pos = cumsum(Classifications)-0.5*Classifications)
df.summary$UserLevel <- factor(df.summary$UserLevel, levels= c("Neutron Star Mountain","Galactic Supernova","Neutron Star Merger","Black Hole Merger","Universe Cosmic Background"))
  

df.summary2 = classifications_promotion %>% group_by(SubmitLevel,UserLevel) %>%
  summarise(Classifications = length(Classifications)) %>%   # Within each Brand, sum all values in each Category
  mutate(percent = Classifications/sum(Classifications),
       pos = cumsum(percent) - 0.5*percent)
df.summary2$UserLevel <- factor(df.summary2$UserLevel, levels= c("Neutron Star Mountain","Galactic Supernova","Neutron Star Merger","Black Hole Merger","Universe Cosmic Background"))
  
```


```{r promotion, echo=TRUE}
promotions_stats
```

The average work to achieve a workflow. Classifications and Session represent the average number which appears as the minimum for the classification at a level. Likely over estimated in some cases since users might not know when they've reached a new level. 

```{r promotion2, echo=TRUE}
promotions_stats2
```


Read as: 
"The number of annotations in the [insert y-axis workflow] were submitted by N individuals in [insert bar portion]"

```{r promotion3, echo=TRUE}
df.summary2$UserLevel <- factor(df.summary2$UserLevel, levels= c("Neutron Star Mountain","Galactic Supernova","Neutron Star Merger","Black Hole Merger","Universe Cosmic Background"))
ggplot(df.summary2, aes(x=UserLevel, y=Classifications, fill=SubmitLevel)) +
  scale_y_continuous() +
  geom_bar(stat='identity',  width = .7, colour="black", lwd=0.1) +
  coord_flip()+
  labs(y="Count of Annotations Submitted", x="User Level when annotation submitted")

```
